The \dealii Library, Version 9.5

### 2023-06-27 9.5/paper.tex
Add two annotations.

Here is a complete example of an MPI parallel Newton solver that automatically chooses one of the available packages:
\begin{c++}
    using NLSolver = NonlinearSolverSelector<LA::MPI::Vector>;

>>>>

Here is a complete example of an MPI parallel Newton solver that
automatically chooses one of the available packages:
\todo[inline]{The NOX example was nicely indented. Can we do the same
  here? Perhaps if we call the variable \texttt{nl\_solver}?}
\todo[inline]{But separately: Does the code snippet really provide any
  additional value? It is for all practical purposes identical to the
  NOX one, and the NOX one is already identical to the SNES one. Do we
need to repeat things a third time, or could one just use one or two
sentences to express the same?}
\begin{c++}
    using NLSolver = NonlinearSolverSelector<LA::MPI::Vector>;
